---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = "C:/github/snapmeta")
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-", eval = TRUE,
  message = FALSE, warning = FALSE, error = FALSE, tidy = TRUE
)
```

# snapmeta

[![Travis-CI Build Status](https://travis-ci.org/leonawicz/snapmeta.svg?branch=master)](https://travis-ci.org/leonawicz/snapmeta)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/leonawicz/snapmeta?branch=master&svg=true)](https://ci.appveyor.com/project/leonawicz/snapmeta)
[![Coverage Status](https://img.shields.io/codecov/c/github/leonawicz/snapmeta/master.svg)](https://codecov.io/github/leonawicz/snapmeta?branch=master)

`snapmeta` contains a collection of utility functions for the development of other SNAPverse packages.

## Installation

You can install snapmeta from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("leonawicz/snapmeta")
```

## Usage

### Package setup

First, take a look at the helpful reminders in the console output from `new_pkg_reminder`.
It will be somewhat specific to your account and project if you pass arguments.
For example, using my defaults:

```{r reminders}
library(snapmeta)
reminders()
```

This should all be familiar if you develop R packages, but it can be easy to occasionally neglect a step.
The recommendations are not completely universal, however, and cater specifically to SNAPverse package development.

If it meets all needs, run:

```{r use_these, eval = FALSE}
use_these()
```

If something different is needed, ignore the above wrapper function.
Instead, make individual calls to whichever package setup functions are required.

### Getting info from the verse

A table of all SNAPverse packages can be obtained by:

```{r sv_pkgs}
sv_pkgs()
```

The table includes columns giving the section of the verse a package belongs to and whether or not a local git repository/R source package
exists sharing the same parent directory as the current package (current working directory).
A short list of the latter existing local packages can be obtained by:

```{r sv_local_pkgs}
sv_local_pkgs()
```
